### 2019-05-01 README.Rmd
Move to v0.1.1 Update DESCRIPTION to reflect new version number Update README to add in new function (rob_traffic_light) Renamed rob_summary_tools() function to rob_tools()

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "90%",
  fig.width= 12, 
  fig.height=3)
```
# robvis <img src="man/figures/robvis_hex_box.png" align="right" width="18%" height="18%" />

@@

## Description
The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, produces a summary plot (incorporating some measure of weighting for each study), and formats the plot according to the assessment tool used.

The package contains two functions:

@@

### rob_summary_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary(). Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2. We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

@@

**For the RoB2.0 tool for randomized controlled trials:**
```{r}
plot_rob <- rob_summary(data = data_rob, tool = "ROB2")
plot_rob
```

**For the ROBINS-I tool for non-randomised studies of interventions:**
```{r}
plot_robins <- rob_summary(data = data_robins, tool = "ROBINS-I")
plot_robins
```

**For the QUADAS-2 tool for diagnostic accuracy studies:**
```{r}
plot_quadas <- rob_summary(data = data_quadas, tool = "QUADAS-2")
plot_quadas
```

### Include overall risk-of-bias judgements
```{r}
plot_rob <- rob_summary(data = data_robins, tool = "ROBINS-I", overall = TRUE)
plot_rob
```

## Additional usage
Because the output (`plot` in the above examples) is a ggplot2 object, it is easy to adjust the plot to your own preferences.

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-")
```
# robvis <img src="man/figures/robvis_hex_box.png" align="right" width="18%" height="18%" />

@@

## Description
**UPDATE**: `robvis` now exists as a [web-app](https://mcguinlu.shinyapps.io/robvis), aimed at those who are not confident with R/those who want to explore the package's functionality.

The `robvis` package takes the summary table from risk-of-bias assessments, converts it to tidy data, produces a summary plot (incorporating some measure of weighting for each study), and formats the plot according to the assessment tool used.

The package contains three functions:

@@

### rob_traffic_light()
Returns a ggplot object displaying a ["traffic light plot"](https://handbook-5-1.cochrane.org/chapter_8/figure_8_6_c_example_of_a_risk_of_bias_summary_figure.htm), displaying the risk of bias judgement made in each domain for each study.

### rob_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary(). Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2. We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

@@

#### RoB2.0 tool for randomized controlled trials:
```{r out.width = "90%", fig.width= 12, fig.height=3}
plot_rob <- rob_summary(data = data_rob, tool = "ROB2")
plot_rob
```

```{r out.width = "90%", fig.width= 8, fig.height=8}
trafficlight_rob <- rob_traffic_light(data = data_rob, tool = "ROB2")
trafficlight_rob
```

#### ROBINS-I tool for non-randomised studies of interventions:**
```{r}
plot_robins <- rob_summary(data = data_robins, tool = "ROBINS-I")
plot_robins
```

#### QUADAS-2 tool for diagnostic accuracy studies:**
```{r}
plot_quadas <- rob_summary(data = data_quadas, tool = "QUADAS-2")
plot_quadas
```

## Additional usage
Because the output (`plot_tool` in the above examples) is a ggplot2 object, it is easy to adjust the plot to your own preferences.

@@

## Planned updates

* Templates for additional risk of bias tools, including:
  * Cochrane risk of bias tool for randomised controlled trials (RoB Version 1)
  * PROBAST
  * ROBIS
* Ability to specify file type extension when saving image. Priority being Window 
* Additional functionality to specify the element of QUADAS-2 that you want to visualise (applicability or risk of bias)
* Choice of colour schemes (or ability to specify your own colours, have not decided yet)
* Improved text processing to allow for imperfect matching of judgements, primarily to allow for differences in cases (e.g. "low" will match with "Low"" and for minor spelling errors (e.g. "loq" will match with "Low")
* A planned function to provide a brief draft paragraph summarising the risk-of-bias assessment results, which authors can then edit/elaborate on as needed. This element of the project was inspired by the reporter function in `metafor`
